Light versus Dark in Strong Lensing Galaxies: Dark matter halos that are rounder than their stars

### 2014-12-26 shapes/paper.tex
Slightly changed Figure A3

We note in Figure~\ref{fig:lensreconstruction2} specifically for {\it0957} and to some degree also {\it1422} twisting isophotes \citep{1978ComAp...8...27B}. {\bf (CB: DOES THIS NEED TO BE EXPANDED?)}

>>>>

We note in Figure~\ref{fig:lensreconstruction2}, specifically for {\it0957} and to some degree also {\it1422}, twisting isophotes \citep[e.g.][]{1978ComAp...8...27B}.
